Refinements for open pNets

### 2021-07-28 2021-Refinement/paper/refinementarticle.tex
part

On the deadlock prevention aspect, an article by Dihego, Sampaio and Oliveira \cite{DIHEGO2020110598} present a refinement relation on process algebra (translated to LTS).
This refinement relation is a special case of inheritance and prevents the introduction of deadlocks.
Their refinement and inheritance are quite the opposite of our refinement in terms of new behaviours.
They have channels, interfaces, inputs and outputs, which in the open automata model can be compared to action labels, holes and action data for both inputs and outputs.
They have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
In their model there is an explicit deadlock and a succesful termination where in open automata there are no explicit termination.
We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.
To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata compositon.

@@

\begin{definition}[Deadlock reduction]\label{def:dpwd}
Let \(\OAg[1]\), \(\OAg[2]\) be two OAs.
A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
\begin{multline*}
 \forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
\end{definition}

@@

\subsection{Refinement Relations for automata with the same holes}
\TODO{Hole - = relation}

\TODO{pour rabea}

>>>>

On the deadlock prevention aspect, an article by Dihego, Sampaio and Oliveira \cite{DIHEGO2020110598} present a refinement relation on process algebra (translated to LTS).
This refinement relation is a special case of inheritance and prevents the introduction of deadlocks.
Their refinement and inheritance are quite the opposite of our refinement in terms of new behaviours.
They have channels, interfaces, inputs and outputs, which in the open automata model can be compared to action labels, holes and action data for both inputs and outputs.
They have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
In their model there is an explicit deadlock and a successful termination where in open automata there are no explicit termination.
We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.
To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata composition.

@@

\begin{definition}[Deadlock reduction]\label{def:dpwd}\\
Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
\begin{multline*}
 \forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
\end{multline*}
\end{definition}

@@

\subsection{Refinement Relations for automata with the same holes}
\TODO{Hole - = relation pour rabea }

We generalise simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
\begin{definition}[Hole-equal simulation]
Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}
	\end{array}} \\
	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\end{definition}
Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$. Note also the second part of the conjunction of condition 2 expresses the deadlock reduction between automata.

Intuitively, this means that for every pair of related
states $(s_1,s_2)$  of the two automata, and for every each transition of the first automaton from $s_1$, there is a matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
